---
title: "Energy Equity Residential Energy Consumption"
author: "Audrey Smith"
date: 5/8/2020"
output: html_document
---

_Setting up .rmd file_
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Librarying Packages
```{r}
library(tidyverse)
library(survey)
library(fastDummies)
library(sf)
library(data.table)
library(MASS)
options(scipen=999)
```

#Read in Data
Note - there's a big mismatch between what I've hand-calculated as electricity and NG price based on the RECS data and the prices downloaded from the EIA site. I'm fairly certain they are the same units - so unsure what the source of the discrepancy is.
```{r - Read RECS data and set study design}
#Reading in RECS data
recs15 <- read.csv('RECS/recs2015_clean.csv')

#Calculate energy prices
recs15$PRNG <- 10*recs15$DOLLARNG/recs15$CUFEETNG #EIA price is per 1,000 cu ft, this is in 100 cu ft
recs15$PREL <- 100*recs15$DOLLAREL/recs15$KWH #100 is arbitrary and from visually inspecting the data - need to inspect discrepancy
recs15$PRLPG <- recs15$DOLLARLP/recs15$GALLONLP
recs15$PRFO <- recs15$DOLLARFO/recs15$GALLONFO

#Generating weight and rep weights
recsWeights <- recs15$NWEIGHT
recsBrr <- recs15[,grepl('^BRRWT', colnames(recs15))] #Grabbing all columns with Brr weights

generateDes <- function(recs15FUEL){
  recsWeights <- subset(recs15, recs15FUEL > 0) %>% pull(NWEIGHT)
  colsBrr <- subset(colnames(recs15), grepl('^BRRWT', colnames(recs15)) == T)
  recsBrr <- filter(recs15, recs15FUEL > 0) %>% dplyr::select(colsBrr)
  
  recsDes <- svrepdesign(weights = recsWeights, repweights = recsBrr, type = 'Fay', rho = .5, mse = TRUE, data = subset(recs15, recs15FUEL > 0))
  
  return(recsDes)
}

#Setting survey design
recsDes <- svrepdesign(weights = recsWeights, repweights = recsBrr, type = 'Fay', rho = .5, mse = TRUE, data = recs15) 
recsDes_EL <- generateDes(recs15$KWH)
recsDes_NG <- generateDes(recs15$CUFEETNG)
recsDes_LPG <- generateDes(recs15$GALLONLP)
#recsDes_FO <- generateDes(recs15$GALLONFO)
```

```{r - Read in ACS Data}
tractPreds <- read.csv('predictors/ACSclimate_clean.csv') %>% dplyr::select(-X)
tractGeom <- read_sf('predictors/ACS_climateZones_int.shp') %>% dplyr::select(GISJOIN, geometry)

#Need to figure out why so many NAs
tractPreds <- drop_na(tractPreds)

#Add energy prices from EIA
tractPreds$PRNG <- ifelse(tractPreds$state_code == 8, 7.72, ifelse(tractPreds$state_code == 32, 7.89, 9.24))
tractPreds$PREL <- ifelse(tractPreds$state_code == 8, 12.04, ifelse(tractPreds$state_code == 32, 12.47, 12.12))
```

#Plotting Response Variables
```{r}
#Electricity
svyhist(~KWH, recsDes)
svyhist(~log(KWH+.0000001), recsDes)
svyhist(~sqrt(KWH), recsDes)

#Natural Gas
svyhist(~CUFEETNG, recsDes)
svyhist(~log(CUFEETNG+.000001), recsDes)
svyhist(~sqrt(CUFEETNG), recsDes)

#Liquid Propane
svyhist(~GALLONLP, recsDes)
svyhist(~log(GALLONLP+.0000001), recsDes)
svyhist(~sqrt(GALLONLP), recsDes)

#Fuel Oil
svyhist(~GALLONFO, recsDes)
svyhist(~log(GALLONFO + .0000001), recsDes)
svyhist(~sqrt(GALLONFO), recsDes)

#Wood
svyhist(~WOODAMT, recsDes)
svyhist(~log(WOODAMT + .0000001), recsDes)
svyhist(~sqrt(WOODAMT), recsDes)
```

lpgLog_full <- svyglm(log(BTULP+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + TOTROOMS + TOTROOMSSQ + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5+ EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7, family = gaussian(identity), design = recsDes_LPG)

## Log Models by Fuel Type
```{r}
### ELECTRICITY ###
#Full
elecLog_full <- svyglm(log(BTUEL+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5 + FUELHEAT_7 + PREL + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + HOUSEHOLDER_RACE_2 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + HOUSEHOLDER_RACE_5 + HOUSEHOLDER_RACE_7 + TOTROOMS + TOTROOMSSQ + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7 + YEARMADERANGE_8 + TYPEHUQ_1 + TYPEHUQ_3 + TYPEHUQ_4 + TYPEHUQ_5 + ELPAY_1 + HEATHOME, family = gaussian(identity), design = recsDes_EL)

#Select
elecLog <- stepAIC(object = elecLog_full, direction = 'backward', trace = F)
elecLog_MSE <- c(crossprod(elecLog$residuals))/length(elecLog$residuals)

#Predict
predict_elecLog <- as.data.frame(predict(object = elecLog, newdata = tractPreds, type = 'response', na.action = na.include))
predict_elecLog$BTUelec <- 1000*exp(predict_elecLog$response)

### NATURAL GAS ###
#Full
ngLog_full <- svyglm(log(BTUNG+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5 + FUELHEAT_7 + PRNG + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + TOTROOMS + TOTROOMSSQ + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7 + YEARMADERANGE_8+ TYPEHUQ_1 + TYPEHUQ_3 + TYPEHUQ_4 + TYPEHUQ_5 + HOUSEHOLDER_RACE_2 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + HOUSEHOLDER_RACE_5 + ELPAY_1, family = gaussian(identity), design = recsDes_NG)

#Log
ngLog <- stepAIC(object = ngLog_full, direction = 'backward', trace = F)
ngLog_MSE <- c(crossprod(ngLog$residuals))/length(ngLog$residuals)

#Predict
predict_ngLog <- as.data.frame(predict(object = ngLog, newdata = tractPreds, type = 'response', na.action = na.exclude))
predict_ngLog$BTUng <- 1000*exp(predict_ngLog$response)

### LIQUID PROPANE GAS ###
#Full
lpgLog_full <- svyglm(log(BTULP+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5 + FUELHEAT_7 + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + HOUSEHOLDER_RACE_2 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + HOUSEHOLDER_RACE_5 + HOUSEHOLDER_RACE_7 + TOTROOMS + TOTROOMSSQ + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7 + YEARMADERANGE_8 + TYPEHUQ_1 + TYPEHUQ_3 + TYPEHUQ_4 + TYPEHUQ_5 + ELPAY_1 + HEATHOME, family = gaussian(identity), design = recsDes)

#Log
lpgLog <- stepAIC(object = lpgLog_full, direction = 'backward', trace = F)
lpgLog_MSE <- c(crossprod(lpgLog$residuals))/length(lpgLog$residuals)

#Predict
predict_lpgLog <- as.data.frame(predict(object = lpgLog, newdata = tractPreds, type = 'response', na.action = na.exclude))
predict_lpgLog$BTUlpg <- 1000*exp(predict_lpgLog$response)

### FUEL OIL ###
#Full
foLog_full <- svyglm(log(BTUFO+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5 + FUELHEAT_7 + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + HOUSEHOLDER_RACE_2 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + HOUSEHOLDER_RACE_5 + HOUSEHOLDER_RACE_7 + TOTROOMS + TOTROOMSSQ + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7 + YEARMADERANGE_8 + TYPEHUQ_1 + TYPEHUQ_3 + TYPEHUQ_4 + TYPEHUQ_5 + ELPAY_1 + HEATHOME, family = gaussian(identity), design = recsDes)

#Log
foLog <- stepAIC(object = foLog_full, direction = 'backward', trace = F)
foLog_MSE <- c(crossprod(foLog$residuals))/length(foLog$residuals)

#Predict
predict_foLog <- as.data.frame(predict(object = foLog, newdata = tractPreds, type = 'response', na.action = na.exclude))
predict_foLog$BTUfo <- 1000*exp(predict_foLog$response)

### WOOD ###
#Full
woodLog_full <- svyglm(log(WOODBTU+.0000000001) ~ DIVISION_8 + CLIMATE_HOTDRY + FUELHEAT_1 + FUELHEAT_2 + FUELHEAT_5 + FUELHEAT_7 + HDD65 + CDD65 + HHAGE + HHSEX_1 + log(NHSLDMEM) + NUMCHILD + EMPLOYHH_12 + SDESCENT_1 + MONEYPY_2 + MONEYPY_3 + MONEYPY_45 + MONEYPY_678 + HOUSEHOLDER_RACE_2 + HOUSEHOLDER_RACE_3 + HOUSEHOLDER_RACE_4 + HOUSEHOLDER_RACE_5 + HOUSEHOLDER_RACE_7 + TOTROOMS + TOTROOMSSQ + YEARMADERANGE_2 + YEARMADERANGE_3 + YEARMADERANGE_4 + YEARMADERANGE_5 + YEARMADERANGE_6 + YEARMADERANGE_7 + YEARMADERANGE_8 + TYPEHUQ_1 + TYPEHUQ_3 + TYPEHUQ_4 + TYPEHUQ_5 + ELPAY_1 + HEATHOME, family = gaussian(identity), design = recsDes)

#Log
woodLog <- stepAIC(object = woodLog_full, direction = 'backward', trace = F)
woodLog_MSE <- c(crossprod(woodLog$residuals))/length(woodLog$residuals)

#Predict
predict_woodLog <- as.data.frame(predict(object = woodLog, newdata = tractPreds, type = 'response', na.action = na.exclude))
predict_woodLog$BTUwood <- 1000*exp(predict_woodLog$response)
```

_All Fuels_
```{r}
predict_allLog <- as.data.frame(cbind(tractPreds[,c(1, 14, 19, 18)], predict_elecLog, predict_ngLog, predict_lpgLog, predict_foLog, predict_woodLog))
predict_allLog <- predict_allLog[, c(1:4, 7, 10, 13, 16, 19)]
expected <- c(343000000000000, 165000000000000, 112000000000000)

predict_allLog %>%
  mutate_at(.vars = c('BTUelec', 'BTUng', 'BTUlpg', 'BTUfo', 'BTUwood'), .funs = function(x){x*predict_allLog$TOTALHH}) #%>%
  #write.csv('output/output_May29_byHH.csv')

predict_allLog %>%
  mutate(BTUtract = TOTALPOP*(BTUelec + BTUng + BTUlpg + BTUfo + BTUwood)) %>%
  group_by(state_code) %>%
  summarize(BTUstate = sum(BTUtract)) %>%
  mutate(BTUexpected = expected, propUnder = (BTUexpected-BTUstate)/BTUexpected)

print(paste('R2 elec:', with(summary(elecLog), 1-deviance/null.deviance)))
print(paste('R2 natural gas:', with(summary(ngLog), 1-deviance/null.deviance)))
print(paste('R2 liquid propane:', with(summary(lpgLog), 1-deviance/null.deviance)))
print(paste('R2 fuel oil:', with(summary(foLog), 1-deviance/null.deviance)))
print(paste('R2 wood:', with(summary(woodLog), 1-deviance/null.deviance)))
```
